Data Formatting

### 2021-05-27 scripts/data_format.Rmd
working on code for eeid poster

Phylogeny
```{r}
resolved <- tnrs_match_names(names$tnrs_name)
resolved %<>% rename("tnrs_name" = "unique_name")
#resolved$search_string <- paste(toupper(substr(resolved$search_string, 1, 1)), 
#                                  substr(resolved$search_string,2,nchar(resolved$search_string)),sep = "")

@@

names %<>% filter(tnrs_name!="Dryophytes avivoca") #drop species because there is no abundance data
mySpp <- c(union(names$tnrs_name,names$species_name),"Bufo terrestris") #make vector for all species names
mySpp <- gsub(" ","_",mySpp)
getRid <- setdiff(tree$tip.label,mySpp)
pruned_tree <- drop.tip(tree,getRid)

>>>>

Phylogeny
```{r}
rv_sampled <- data %>% select(Species) %>% distinct() #species codes for those sampled for rv
rv_sampled %<>% filter(Species!=32) #remove species 32 because there is no abundance data
keep <- c(rv_sampled$Species)

resolved <- tnrs_match_names(names$tnrs_name)
resolved %<>% rename("tnrs_name" = "unique_name")
#resolved$search_string <- paste(toupper(substr(resolved$search_string, 1, 1)), 
#                                  substr(resolved$search_string,2,nchar(resolved$search_string)),sep = "")

@@

names %<>% filter(species_code %in% keep)

names %<>% filter(tnrs_name!="Dryophytes avivoca") #drop species because there is no abundance data
mySpp <- c(union(names$tnrs_name,names$species_name),"Bufo terrestris") #make vector for all species names
mySpp <- gsub(" ","_",mySpp)
getRid <- setdiff(tree$tip.label,mySpp)
pruned_tree <- drop.tip(tree,getRid)
```
